---
title: "TestAnalyzer"
output: html_document
---

Common Operations/Calculations for Hypothesis test analysis
```{r common calculations}
is.sig <- function(p.value) {
   if(p.value<0.05) {
   return("yes")
  } else {
    return("no")
  } 
}

getConfidenceInterval <- function(start,end) {
  return(paste(start,end,sep=" to "))
}

getIndex <- function(val1,val2) {
  return(val1/val2-1)
}

```

Assume two-tailed

**Function for Z-test given known number of success samples and total sample size**

x1 = number of successes in control group
x2 = number of successes in test group
n1 = number of samples in control group
n2 = number of samples in test group

```{r z-test}
z.test.fromdata <- function(x1,x2,n1,n2) {
  
  #call r package for two prop z-test
  results <- prop.test(c(x1,x2),c(n1,n2),correct=FALSE)
  results_onesided <- prop.test(c(x1,x2),c(n1,n2),alternative = "greater",correct=FALSE)
  
  prop1 <- results$estimate["prop 1"]
  prop2 <- results$estimate["prop 2"]
  
  #create named list
  ret <- as.list(c(round(prop1,digits = 4),round(prop2,digits=4), round(results$p.value,digits=4),round(results_onesided$p.value,digits=4),getConfidenceInterval(round(results$conf.int[1],digits=4),round(results$conf.int[2],digits=4)),round(getIndex(prop1,prop2),digits=4),is.sig(results$p.value)))
  names(ret) <- c("Test_proportion","Control_proportion", "p-value_two-sided", "p-value_one-sided","Confidence_Interval_95_perc","Index","Significant")
  
  return(ret)
}
```

**Function for T-test given two data input vectors**

controldata = vector of control data
testdata = vector of test data

```{r t-test from data}
t.test.fromdata <- function(controldata,testdata) {
  
  #call r package for two prop t-test
  results <- t.test(controldata,testdata,var.equal=TRUE,paired=FALSE)
  results_onesided <- t.test(controldata,testdata,alternative = "greater", var.equal=TRUE,paired=FALSE)
  
  m1 <- results$estimate["mean of x"]
  m2 <- results$estimate["mean of y"]
  
  #create named list
  ret <- as.list(c(round(m1,digits=4),round(m2,digits=4),round(results$p.value,digits=4),round(results_onesided$p.value,digits=4),getConfidenceInterval(round(results$conf.int[1],digits=4),round(results$conf.int[2],digits=4)),  round(getIndex(m1,m2),digits=4),is.sig(results$p.value)))
  names(ret) <- c("Test_mean","Control_mean", "p-value_two-sided", "p-value_one-sided","Confidence_Interval_95_perc","Index","Significant")
  
  return(ret)
}
```


**Function for T-test given known sample size, mean, and standard deviations input**

m1, m2: the sample means
s1, s2: the sample standard deviations
n1, n2: the same sizes
m0: the null value for the difference in means to be tested for. Default is 0. 
equal.variance: whether or not to assume equal variance. Default is FALSE. 

```{r t-test from values}
t.test.fromvalues <- function(m1,m2,s1,s2,n1,n2,equal.variance=TRUE) {
 
   #calculations
  if( equal.variance==FALSE ) {
    se <- sqrt( (s1^2/n1) + (s2^2/n2) )
    df <- ( (s1^2/n1 + s2^2/n2)^2 )/( (s1^2/n1)^2/(n1-1) + (s2^2/n2)^2/(n2-1) )
  } else {
    se <- sqrt( (1/n1 + 1/n2) * ((n1-1)*s1^2 + (n2-1)*s2^2)/(n1+n2-2) ) 
    df <- n1+n2-2
  }  
  
  t <- (m1-m2)/se
  
  p.value <- round(2*pt(-abs(t),df),digits=4)
  p.value.one.sided <- round(pt(-abs(t),df),digits=4)
  diff <- m1-m2
  
  confint.start <- round(diff - abs(qt(0.05/2,df))*se,digits=4)
  confint.end <- round(diff + abs(qt(0.05/2,df))*se,digits=4)
  
  #create named list
  ret <- as.list(c(round(m1,digits=4),round(m2,digits=4),p.value,p.value.one.sided, getConfidenceInterval(confint.start,confint.end),round(getIndex(m1,m2),digits=4),is.sig(p.value)))
  names(ret) <- c("Test_mean","Control_mean", "p-value_two-sided", "p-value_one-sided","Confidence_Interval_95_perc","Index","Significant")

  return(ret) 
}
```